Type Refinements for the Working Class

### 2015-12-19 paper.tex
unambiguous naming
closure -> value closure

Now, let us return briefly to Martin-L\"of's notion of type, which we call a
\emph{value type}. The minimal data of such a type's definition consists in a
partial equivalence relation on values,
$\Of{\phi}{\Hom{\Sets^\SCtx}{\Coyoneda{\Upsilon}}{\PERs{\Values_\tau}}}$.
It is easy to turn such a relation into a computational type
$\IsType{\Upsilon}{\VToCType(\phi)}{\tau}$, as follows:
\[
  \begin{tikzcd}[sep=huge]
    \IMode{\Coyoneda{\Upsilon}\times\Values_\tau^2}
      \arrow[r, "\IMode{\lambda(\phi)}"]
      \arrow[d, swap, "\IMode{\Pair{\ArrId{}}{\iota}}"]
      &
    \IMode{\Omega}\\
    \IMode{\Coyoneda{\Upsilon}\times\Exprs_\tau^2}
    \arrow[ur, swap, dotted, "\OMode{\lambda(\VToCType(\phi))}"]
  \end{tikzcd}
\]
where $\VToCType(\phi)$ is the computational extension of $\phi$ in the following sense:
\begin{align*}
  \ADefine{
    \VToCType(\phi)(M,N)
  }{
    \forall M', N' \in \Values_\tau.\
    M\sim_\tau M' \land N\sim_\tau N' \implies \phi(M',N')
  }
\end{align*}

@@

\begin{definition}[Closure]
  For any computational type $\IsType{\Upsilon}{\phi}{\tau}$, let
  $\Define{\underline{\phi}}{\VToCType(\iota(\phi))}$ be called $\phi$'s
  \emph{closure}, which we will use shortly in order to give a formal definition
  to the notion of value types.
\end{definition}

\begin{definition}[Value Types]
  We can give a simple characterization of Martin-L\"of's \emph{value types} in
  terms of our more general computational types. For any type $\IsType{\Upsilon}{\phi}{\tau}$,
  we will say $\IsValueType{\Upsilon}{\phi}{\tau}$ in case $\phi$ is equal to
  its closure, i.e.\ $\EqRefines{\Upsilon}{\phi}{\underline{\phi}}{\tau}$.
\end{definition}

>>>>

Now, let us return briefly to Martin-L\"of's notion of type, which we call a
\emph{value type}. The minimal data of such a type's definition consists in a
partial equivalence relation on values,
$\Of{\phi}{\Hom{\Sets^\SCtx}{\Coyoneda{\Upsilon}}{\PERs{\Values_\tau}}}$.
It is easy to turn such a relation into a computational type
$\IsType{\Upsilon}{\VToCType(\phi)}{\tau}$, as follows:
\[
  \begin{tikzcd}[sep=huge]
    \IMode{\Coyoneda{\Upsilon}\times\Values_\tau^2}
      \arrow[r, "\IMode{\lambda(\phi)}"]
      \arrow[d, hook, swap, "\IMode{\Pair{\ArrId{}}{i}}"]
      &
    \IMode{\Omega}\\
    \IMode{\Coyoneda{\Upsilon}\times\Exprs_\tau^2}
    \arrow[ur, swap, dotted, "\OMode{\lambda(\VToCType(\phi))}"]
  \end{tikzcd}
\]
where $\VToCType(\phi)$ is the computational extension of $\phi$ in the following sense:
\begin{align*}
  \ADefine{
    \VToCType(\phi)(M,N)
  }{
    \forall M', N' \in \Values_\tau.\
    M\sim_\tau M' \land N\sim_\tau N' \implies \phi(M',N')
  }
\end{align*}

@@

\begin{definition}[Value Closure]
  For any computational type $\IsType{\Upsilon}{\phi}{\tau}$, let
  $\Define{\underline{\phi}}{\VToCType(\iota(\phi))}$ be called $\phi$'s
  \emph{value closure}, which we will use shortly in order to give a formal definition
  to the notion of value types.
\end{definition}

\begin{definition}[Value Types]
  We can give a simple characterization of Martin-L\"of's \emph{value types} in
  terms of our more general computational types. For any type $\IsType{\Upsilon}{\phi}{\tau}$,
  we will say $\IsValueType{\Upsilon}{\phi}{\tau}$ in case $\phi$ is equal to
  its value closure, i.e.\ $\EqRefines{\Upsilon}{\phi}{\underline{\phi}}{\tau}$.
\end{definition}
